\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-07-21 paper.qmd
Update MNIST PaCMAP Figure title

Model in \gD{}, on the UMAP layout, and three views of the fit in projections from $9\text{-}D$, for the PBMC3k data ($(s_1, \ s_2) = (-0.050, \ 0.041)$, $b = 870 \  (30, \ 29)$, $m = 135$, benchmark value to remove large edges is $0.099$). (The **langevitour** software is used to view the data with a tour, and the full video is available at <https://youtu.be/VqqWuE0Jj6A>).
:::

>>>>

Model in \gD{}, on the UMAP layout, and three views of the fit in projections from $9\text{-}D$, for the PBMC3k data ($(s_1, \ s_2) = (-0.050, \ -0.041)$, $b = 870 \  (30, \ 29)$, $m = 135$, benchmark value to remove large edges is $0.099$). (The **langevitour** software is used to view the data with a tour, and the full video is available at <https://youtu.be/VqqWuE0Jj6A>).
:::

### 2024-07-21 paper.tex
Update MNIST PaCMAP Figure title

\caption{\label{fig-pbmc1-sc}Model in \gD{}, on the UMAP layout, and
three views of the fit in projections from \(9\text{-}D\), for the
PBMC3k data (\((s_1, \ s_2) = (-0.050, \ 0.041)\),
\(b = 870 \  (30, \ 29)\), \(m = 135\), benchmark value to remove large
edges is \(0.099\)). (The \textbf{langevitour} software is used to view
the data with a tour, and the full video is available at
\url{https://youtu.be/VqqWuE0Jj6A}).}

>>>>

\caption{\label{fig-pbmc1-sc}Model in \gD{}, on the UMAP layout, and
three views of the fit in projections from \(9\text{-}D\), for the
PBMC3k data (\((s_1, \ s_2) = (-0.050, \ -0.041)\),
\(b = 870 \  (30, \ 29)\), \(m = 135\), benchmark value to remove large
edges is \(0.099\)). (The \textbf{langevitour} software is used to view
the data with a tour, and the full video is available at
\url{https://youtu.be/VqqWuE0Jj6A}).}
